Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-17 paper_jasa.tex
figure caption
colour mentioned

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_definition.pdf}}
       \caption{Conventional test $p$-value ($p_D$) vs visual $p$-value obtained from the definition . Values are shown on square root scale. For experiment 3, $p$-values of uncontaminated part of the data are also shown.}
    %   \hh{Mahbub, another change: could you change the y label to 'estimate of visual p-value $\hat{p_D}$ ?}
       \label{fig:pval_definition}
\end{figure*}

@@

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_log_counts.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the sixty (60) individual lineups for experiment 1. Red indicates the plot with the lowest $p$-value, and blue indicates the actual data plot, when it is different from that with the lowest $p$-value. Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value.}
       \label{fig:P-val_log}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_log_counts2.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the seventy (70) individual lineups for experiment 2. Red indicates the plot with the lowest $p$-value, and blue indicates the actual data plot, when it is different from that with the lowest $p$-value. Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value, even more so than for experiment 1.}
       \label{fig:P-val_log2}
\end{figure*}

>>>>

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_definition.pdf}}
       \caption{Conventional test $p$-value ($p_D$) vs visual $p$-value obtained from the definition . Values are shown on square root scale. }
    %   \hh{Mahbub, another change: could you change the y label to 'estimate of visual p-value $\hat{p_D}$ ?}
       \label{fig:pval_definition}
\end{figure*}

@@

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_log_counts.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the sixty (60) individual lineups for experiment 1. \blue{Red indicates the} plot with the lowest $p$-value, and \blue{blue indicates the} actual data plot, when it is different from that with the lowest $p$-value. Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value.}
       \label{fig:P-val_log}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_log_counts2.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the seventy (70) individual lineups for experiment 2. \blue{Red indicates the} plot with the lowest $p$-value, and \blue{blue indicates} the actual data plot, when it is different from that with the lowest $p$-value. Rows correspond to $\beta$, smallest to largest values from top to bottom. Columns correspond to other experimental treatments, sample size $(n)$, error standard deviation $(\sigma)$, and replicate. Empty cells indicate no lineup for that combination of parameters. Highest counts tend to be the plot in the lineup having the lowest $p$-value, even more so than for experiment 1.}
       \label{fig:P-val_log2}
\end{figure*}
